---
title: "Metabolism Modeling"
author: "Nick Marzolf and Jonny Behrens"
date: "`r Sys.Date()`"
output: html_document
---

# Set Up

```{r setup, echo = FALSE, warning= FALSE, message=FALSE, results='hide', include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

## Clear environment
#rm(list = ls())

## Set project directory 
projdir <- getwd() # Make sure you have the R Project open! 

```

# Preparing Data for Modeling
## Step 1

This will source in all functions (except this workflow) into the Global Env ----

```{r}
scripts <- list.files('code/', 
                      pattern = '*.R', 
                      full.names = TRUE)
# exclude this script!
scripts <- scripts[!scripts %in% 'code/workflow.R']

# source them in 
sapply(scripts, source, .GlobalEnv)
```

## Step 2

Before you model  ----

```{r}
## this fun installs streamMetabolizer (and dependencies) and rstan (and dependencies) from github
prep_bayes_model()

# if this returns an error, running this below will suffice
# install.packages("StanHeaders", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))
# install.packages("rstan", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))
# remotes::install_github("https://github.com/appling/unitted")
# remotes::install_github("https://github.com/USGS-R/streamMetabolizer")

# Load in the remaining packages
library('tidyverse')
library('rstan')
library('StanHeaders')
library('unitted')
library('streamMetabolizer')
library(StreamPULSE)

#install.packages(c('cli', 'fansi', 'vctrs'))
lapply(c('cli', 'fansi', 'vctrs'), library, character.only = TRUE)
```

## Step 3

Find your sites ----
 
```{r}
#this will show you all the stream pulse sites for a given region, in this case North Carolina
sp_sites <- StreamPULSE::query_available_data(region = 'NC') 

# you can define your sites from sp_sites or define your sites if you know them
my_sites <- c('NC_NHC')

```

## Step 4

Get the data ----

```{r}
# get and save the data from streampulse
get_sp_data(sitecode = 'NC_NHC', startdate= "2020-09-30", enddate= "2023-03-01")
```

Format for modeling ---- This is where we add in the rating curve for NHC
 - Data from `pre_sp_data` function is saved here: 'data/raw/{site}_raw.rds'
 
```{r}
## this is a wrapper around StreamPULSE::prep_metabolism
## there are more arguments to modify within this function, check them out ?prep_metabolism
prep_sp_data_v2()
```

# Model in MLE
## Step 5

model and evaluate using MLE ----

```{r}
# the user will have to define which years (calendar) they are interested in
model_mle(years = 2017:2022)
```

```{r}
# evaluate the MLE outputs
eval_mle()
```

# Some Exploration Before In Depth Modeling

```{r}
NC_NHC_raw <- readRDS("data/raw/NC_NHC_raw.rds")

NC_NHC<-NC_NHC_raw$data %>%
  pivot_wider(names_from = "variable", values_from = "value") %>% 
  mutate(year = year(DateTime_UTC)) %>% 
  mutate(day = as.Date(DateTime_UTC)) 

NC_NHC_Daily<-NC_NHC %>% 
  filter(flagtype != "Bad Data") %>% 
  group_by(day, site) %>%
  summarize(across(`DO_mgL`:`AirPres_kPa`, mean), .groups = "keep") %>% 
  mutate(year = year(day)) %>% 
  mutate(data_missing = if_else(is.na(WaterPres_kPa)|is.na(WaterTemp_C)|is.na(DO_mgL)|is.na(AirPres_kPa), "y", "n"))

plot1<-NC_NHC_Daily %>% 
  ggplot(aes(data_missing)) +
  geom_bar() +
  theme_classic() +
  facet_wrap(~year) +   
  theme(legend.position = "bottom") 
plot1


for(i in c(3:6)) {                              # Printing ggplot within for-loop

  plots<-NC_NHC_Daily %>% 
    rename(value = i) %>% 
    ggplot(aes(x= day, y = value, color=year)) +
    geom_point() +
    theme_classic() +
  #  facet_wrap(~year) +   
    ylab(paste(colnames(NC_NHC[i]))) + 
    labs(title = paste(colnames(NC_NHC_Daily[i]), " vs. Time")) +
    theme(legend.position = "bottom") 
  
  print(plots)
}
```

```{r}
for(i in c(6:9)) {                              # Printing ggplot within for-loop

  plots<-NC_NHC %>% 
    rename(value = i) %>% 
    ggplot(aes(x= DateTime_UTC, y = value, color=flagtype)) +
    geom_point() +
    theme_classic() +
  #  facet_wrap(~year) +   
    ylab(paste(colnames(NC_NHC[i]))) + 
    labs(title = paste(colnames(NC_NHC[i]), " vs. Time")) +
    theme(legend.position = "bottom") 
  
  print(plots)
}
```


# Model in Bayes
##Step 6

model in Bayes ----

`model_bays` function is the default
`model_bays_nhc` function is specific to NHC

```{r}

#model_bayes(years = 2021:2023)

model_bayes_nhc(years = 2017:2022)
```

## Step 7

Prepare the usable outputs ----

`diag_bayes` function output is stored in: data/model_runs/Bayes/diag_metab.csv

```{r}
# Find bad data in annual outputs
diag_bayes()
```

`estimate_bayes` function output is stored in: 
 - Site year specific: data/model_runs/Bayes/neon_metab_{site}_{year}.csv
 - Compiled into one file: data/model_runs/Bayes/metab_estimates.csv
 
```{r}
# compile outputs
estimate_bayes()
```

`filter_bayes` function output is stored in: data/filtered_estimates/filtered_metab_estimates.csv
 
```{r}
# filter out bad data from outputs
filter_bayes()

#This code might have a bug: an extra "/" in the output directory
```

# Merge Data

Merge together yearly data into a combined folder for Bayes.

The following code will give an error if it has already been run and the files already are created!

```{r}
Bayes_data_folder<-"data/model_runs/Bayes/"
# get a list of all subfolders in the parent folder
subfolders <- c("daily", "datadaily", "estimates")

# create directory
combined_dir <- 'data/model_runs/Bayes/combined/'
dir.create(combined_dir)
    
# loop through each subfolder
for (i in 1:length(subfolders)) {

  # subfolder name
  subfolder_name<-paste0(Bayes_data_folder, subfolders[i])
  
  # get a list of all CSV files in the subfolder
  csv_files <- list.files(subfolder_name, pattern = ".csv")

  # loop through each CSV file and read it into a dataframe
  dfs <- list()
  for (j in 1:length(csv_files)) {
    df <- read.csv(paste0(subfolder_name, "/", csv_files[j]))
    dfs[[j]] <- df }

  # combine all dataframes into a single dataframe
  combined_df <- dplyr::bind_rows(dfs)

  # create a unique filename for the output CSV file
  output_file <- paste0(str_remove_all(subfolder_name, Bayes_data_folder), "_combined", ".csv")

  # write the combined dataframe to a new CSV file in the subfolder
  write.csv(combined_df, file = paste0(Bayes_data_folder, "combined/", output_file), row.names = FALSE)

}
```
```

