---
title: "Metabolism_Unified"
author: "Jonny Behrens"
date: "`r Sys.Date()`"
output: pdf_document
---

# Overview

This code cleans up the metabolism data, ran on a few different days.

The raw data (and code for each day ran) is saved in a subfolder where this code is saved.

# Set Up Environment

```{r setup, echo = FALSE, warning= FALSE, message=FALSE, results='hide'}
# Set working directory. Ensure the .here file is stored in desired working directory
knitr::opts_knit$set(root.dir = here::here())

# Some knit settings 
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

## Clear environment
rm(list = ls())

## Libraries
library(pacman)
p_load(dplyr,ggplot2,tidyr,StreamPULSE,treemapify,ggpmisc,
       dataRetrieval,lubridate,scales,imputeTS,zoo, ggpubr, tidyverse)
```

```{r}
# Set the start and end dates
start_date <- as.Date("2021-04-01")
end_date <- as.Date("2022-03-31")

# Set colors
PNAS_green<-"#7BB97A"
PNAS_brown<-"#C59883"

# Custom date breaks for time series data
scale_date<-scale_x_date(date_breaks = "1 month",
                 labels = label_date_short(format = c("%Y", "%b", NA, NA)),
                 expand = c(0.005,0.005)) 

scale_date2<-scale_x_date(date_breaks = "2 months",
                 labels = label_date_short(format = c("%Y", "%b", NA, NA)),
                 expand = c(0.005,0.005)) 
```

# Load and Clean Data

```{r}
data_f<-"Metabolism/"
```

## Flow Data

### Instantaneous

```{r}
Discharge_Instant<-read_csv("Metabolism/Discharge_INSTANT_Clean_2024-3-15.csv") %>% 
    mutate(Year = year(Date_UTC)) %>% 
    mutate(Site = case_when(site == "nhc" ~ "forested",
                          site == "ecgs" ~ "wastewater dominated",
                          site == "ecng" ~ "stormwater dominated"))
```

Find SD for calendar year at each site

```{r}
discharge_SD<-Discharge_Instant %>% 
  mutate(SD = sd(InstantDischarge_m3s, na.rm = T),
            .by = c("Site", "Year")) %>% 
  summarize(max_Q = max(InstantDischarge_m3s, na.rm = T), 
         min_Q = min (InstantDischarge_m3s, na.rm = T),
         Difference = max_Q - min_Q, 
         .by = c("Site", "Date_UTC", "SD")) %>% 
  mutate(discharge_exceed_1sd = if_else(Difference > SD, "Exceed 1 SD", "Does Not Exceed 1 SD"),
         discharge_exceed_2sd = if_else(Difference > 2*SD, "Exceed 2 SD", "Does Not Exceed 2 SD")) %>% 
  rename(date = Date_UTC)
```


### Daily: Ellerbe Gage

```{r}
# # Load in file names
# filenames<-list.files(paste0(data_f, "Metabolism_2-2023/data/model_runs/Bayes/datadaily"),
#                       pattern="*.csv", full.names = TRUE) 
# 
# # Remove NHC
# files_to_remove <- grep("NHC", filenames)
# filtered_filenames <- filenames[-files_to_remove]
# 
# # Combine into a list
# l <- lapply(filtered_filenames, read_csv)
# 
# # Clean up names
# short_names<-filtered_filenames %>%
#   str_remove("data/model_runs/Bayes/datadaily/") %>%
#   str_remove(data_f) %>% 
#   str_remove(".csv")
# 
# names(l)<-short_names
# 
# # bind into 1 data.table, by columnname, fill missing with NA
# EC_Q <- data.table::rbindlist( l, use.names = TRUE, fill = TRUE, idcol=short_names) %>%
#   rename(source=1) %>%
#   mutate(Site = if_else(str_detect(source, 'NC_EllerbeGlenn'), 'ECGS',
#                         if_else(str_detect(source, 'NC_EllerbeClub'), 'ECNG', NA_character_)),
#          .after=1)
```

### Daily: NHC

```{r}
# filenames<-list.files(paste0(data_f, "5-6-2023 Run/data/model_runs/Bayes/datadaily"), 
#                         pattern="*.csv", full.names = TRUE)
# 
# l<-lapply(filenames, read_csv)
# 
# short_names<-filenames %>%
#   str_remove("data/model_runs/Bayes/datadaily/") %>%
#   str_remove(data_f) %>% 
#   str_remove(".csv")
# 
# names(l)<-short_names
# 
# NHC_Q <- data.table::rbindlist( l, use.names = TRUE, fill = TRUE, idcol=short_names) %>%
#   rename(source=1) %>%
#   mutate(Site = if_else(str_detect(source, "NC_NHC"), 'NHC', NA_character_),
#          .after=1)
```

```{r}
# discharge<-EC_Q %>% 
#   full_join(NHC_Q) %>% 
#   mutate(Site = case_when(Site == "NHC" ~ "forested",
#                           Site == "ECGS" ~ "wastewater dominated",
#                           Site == "ECNG" ~ "stormwater dominated")) %>% 
#   select(Site, date, discharge.daily) %>% 
#   full_join(discharge_SD) %>% 
#   mutate(discharge_exceed_2sd = if_else(discharge.daily > 2*SD, "Exceed 2 SD", "Does Not Exceed 2 SD")) %>% 
#   select(-SD)
```

## Metabolism 

### Ellerbe Creek

```{r}
# Load in file names
filenames<-list.files(paste0(data_f, "Metabolism_2-2023/data/model_runs/Bayes/daily"),
                      pattern="*.csv", full.names = TRUE) 

# Combine into a list
l <- lapply(filenames, read_csv)

# Clean up names
short_names<-filenames %>%
  str_remove("data/model_runs/Bayes/daily/") %>%
  str_remove(data_f) %>% 
  str_remove(".csv")

names(l)<-short_names

# bind into 1 data.table, by columnname, fill missing with NA
EC_dt <- data.table::rbindlist( l, use.names = TRUE, fill = TRUE, idcol=short_names) %>%
  rename(source=1) %>%
  mutate(Site = if_else(str_detect(source, 'NC_EllerbeGlenn'), 'ECGS',
                        if_else(str_detect(source, 'NC_EllerbeClub'), 'ECNG', NA_character_)),
         .after=1)
```

### New Hope Creek

```{r}
filenames<-list.files(paste0(data_f, "5-6-2023 Run/data/model_runs/Bayes/daily"), 
                        pattern="*.csv", full.names = TRUE)

l<-lapply(filenames, read_csv)

short_names<-filenames %>%
  str_remove("data/model_runs/Bayes/daily/") %>%
  str_remove(data_f) %>% 
  str_remove(".csv")

names(l)<-short_names

NHC_dt <- data.table::rbindlist( l, use.names = TRUE, fill = TRUE, idcol=short_names) %>%
  rename(source=1) %>%
  mutate(Site = if_else(str_detect(source, "NC_NHC"), 'NHC', NA_character_),
         .after=1)
```

### Merge Together and Clean

One question - should we replace unrealistic values (neg GPP, pos ER) with zero 
(as done below), or remove them all together from the dataset 
(equivalent to a day when the model didn't converge)?

```{r}
# Create the time series, to fill missing days
days <- seq.Date(min(NHC_dt$date), max(EC_dt$date), by = "day")

sites<- c("wastewater dominated", "forested", "stormwater dominated") 

time_series_all<-expand.grid(date = days, Site = sites) %>% 
  arrange(date)
  
# Merge together with some cleaning
dt_preclean<-NHC_dt %>% 
  full_join(EC_dt) %>% 
  mutate(Site = case_when(Site == "NHC" ~ "forested",
                          Site == "ECGS" ~ "wastewater dominated",
                          Site == "ECNG" ~ "stormwater dominated")) %>% 
  full_join(time_series_all) %>%
  # Replace unrealistic values (neg GPP and pos ER) with zero
  # Then multiply to convert from units of oxygen to carbon
  mutate(GPP_daily_mean_C = if_else(GPP_daily_mean <= 0, 0, 1.25*GPP_daily_mean),
         ER_daily_mean_C = if_else(ER_daily_mean >= 0, 0, 1.25*ER_daily_mean),
         Net_Metabolism_C = GPP_daily_mean_C + ER_daily_mean_C, # calculate Net metabolism
         .after = date) %>% 
  mutate(Days_Modeled = if_else(is.na(GPP_daily_mean_C), "No Model Output", "Model Converged")) %>% 
  mutate(year = year(date)) %>% 
  mutate(doy = yday(date), .after = date)
```

### Remove high Q days

High flow is defined as being a discharge value that is greater than 1 standard deviations above that site's average discharge.

we will flag days that exceed 1 SD. 

```{r}
dt<-dt_preclean %>% 
  left_join(dplyr::select(discharge_SD, c(Site, date, discharge_exceed_1sd))) %>% 
  mutate(Days_Modeled = case_when(is.na(GPP_daily_mean_C) ~ "No Model Output",
                                  GPP_daily_mean < 0 ~ "GPP/ER Unrealistic", 
                                  ER_daily_mean > 0 ~ "GPP/ER Unrealistic",
                                  discharge_exceed_1sd == "Exceed 1 SD" 
                                                    ~ "Exceeds Discharge Threshold", 
                                  .default = "Passed"))

# NAs for days that do not pass (or for which it wasn't modeled)
dt_filtered<-dt %>% 
  mutate(across(
    .cols = GPP_daily_mean_C:K600_daily_predlog_Rhat,
    .fns = ~ ifelse(Days_Modeled == "Passed", ., NA),
    .names = "{.col}"
  ))
```

Not many of the days, but definitely a few

```{r}
dt %>% 
  dplyr::filter(date > as.Date("2021-04-01") & date < as.Date("2022-05-01")) %>% 
  count(Days_Modeled, Site) %>% 
  pivot_wider(names_from = "Site", values_from = "n") 

dt %>% 
  dplyr::filter(date > as.Date("2021-04-01") & date < as.Date("2022-05-01")) %>% 
  count(Days_Modeled, Site)  %>% 
  mutate(total_count = sum(n), .by = Site) %>%
  mutate(Percent_days = round(100*n/total_count), .keep = "unused") %>% 
  pivot_wider(names_from = "Site", values_from = "Percent_days")
```

# Check Model Performance

## Rhat

As a first pass check, let's check the Rhats of the model outputs.

I like how Rhats are all below 1.05. 

```{r Rhat}
pal_sites<-c('#009E73', '#0072B2', '#D55E00')
names(pal_sites) <- c('forested site', 'wastewater segment', 'stormwater segment') 

dt %>% 
  dplyr::distinct(Site, date, GPP_daily_Rhat, ER_daily_Rhat, K600_daily_Rhat) %>% 
  pivot_longer(names_to = "Measure", values_to = "Rhat", GPP_daily_Rhat:K600_daily_Rhat) %>% 
  mutate(Site = case_when(str_detect(Site, "orest") ~ "forested site",
                          str_detect(Site, "orm") ~ "stormwater segment",
                          str_detect(Site, "aste") ~ "wastewater segment")) %>% 
  ggplot(aes(x = Rhat, color = Site)) + 
  geom_density(position = "dodge") + 
  theme_pubr(legend = "bottom") + 
  facet_wrap(~Measure) + 
  scale_color_manual(values = pal_sites)
```

```{r}
dt %>% 
  dplyr::filter(!is.na(K600_daily_Rhat)) %>% 
  mutate(Rhat_K600_low = if_else(K600_daily_Rhat < 1.05, 1,0), 
         Rhat_ER_low = if_else(ER_daily_Rhat < 1.05, 1,0), 
         Rhat_GPP_low = if_else(GPP_daily_Rhat < 1.05, 1,0)) %>% 
  summarize(n = n(), 
            K600 = sum(Rhat_K600_low), 
            ER = sum(Rhat_K600_low), 
            GPP = sum(Rhat_K600_low)) %>% 
  pivot_longer(names_to = "measure", values_to = "value", K600:GPP) %>% 
  mutate(Percent = 100*value/n)
```

## K600 vs. ER

Next, let's look at the relationship between K600 and ER.  

ideally, if we are not having issues with equifinality, we would expect K600 and ER to not have a clear linear relationship. 

```{r K600ER}
dt %>% 
  mutate(Site = case_when(str_detect(Site, "orest") ~ "forested site",
                          str_detect(Site, "orm") ~ "stormwater segment",
                          str_detect(Site, "aste") ~ "wastewater segment")) %>% 
  ggplot(aes(x = ER_daily_mean, y = K600_daily_mean)) + 
  geom_point(color = "lightgrey") + 
  theme_pubr(legend = "none") + 
  stat_poly_eq(use_label(c("R2"))) +
  stat_poly_line() + 
  facet_wrap(~Site, scales = "free")
```

# Gap Fill

## See Number of Gaps

We can fix it with transmutation and other methods!

```{r}
P_missing_data<-dt_filtered %>% 
  filter(date <= end_date & date >= start_date) %>% 
  mutate_all(~ifelse(is.na(.), 0, .)) %>% 
  ggplot(aes(x=as.Date(date), y=GPP_daily_mean_C, color = Days_Modeled)) +
  geom_point() + 
  scale_date +
  scale_color_manual(values = c("No Model Output" = "red",
                                "GPP/ER Unrealistic" = "purple",
                                "Exceeds Discharge Threshold" = "orange",
                                "Passed" = "blue")) + 
  facet_wrap(~Site, ncol = 1) +
  theme_pubr() + 
  theme(legend.position = "bottom") + labs(x = NULL)

P_missing_data
```

## Create Quantile Range and Transmuted Values (separately)

```{r}
dt_2_597_5<-dt_filtered %>% 
  ungroup() %>% 
  # Clean up data
  filter(GPP_daily_mean_C >= 0) %>% filter(ER_daily_mean_C <= 0) %>% 
  group_by(doy, Site) %>% 
  # Calculate the 2.5% and 97.5% quantile ranges, using daily data
  mutate(GPP_DOY_2_5_C_day = quantile(GPP_daily_mean_C, 0.025, names = FALSE),
         GPP_DOY_97_5_C_day = quantile(GPP_daily_mean_C, 0.975,names = FALSE),
         ER_DOY_2_5_C_day = quantile(ER_daily_mean_C, 0.025,names = FALSE),
         ER_DOY_97_5_C_day = quantile(ER_daily_mean_C, 0.975,names = FALSE), 
         NetMetab_DOY_2_5_C_day = quantile(Net_Metabolism_C, 0.025,names = FALSE),
         NetMetab_DOY_97_5_C_day = quantile(Net_Metabolism_C, 0.975,names = FALSE), 
         .after = Net_Metabolism_C) %>% 
  # Keep unique rows, for each site and doy
  distinct(Site,doy, GPP_DOY_2_5_C_day,GPP_DOY_97_5_C_day,ER_DOY_2_5_C_day,
           ER_DOY_97_5_C_day, NetMetab_DOY_2_5_C_day,NetMetab_DOY_97_5_C_day) %>% 
  # Calculate the 2.5% and 97.5% quantile ranges, based on 3-day rolling average
  group_by(Site) %>% 
  arrange(Site, doy) %>% 
  mutate(GPP_DOY_2_5_C = rollmean(GPP_DOY_2_5_C_day, k=3, fill=NA, align = "right"),
         GPP_DOY_97_5_C = rollmean(GPP_DOY_97_5_C_day, k=3, fill=NA, align = "right"),
         ER_DOY_2_5_C = rollmean(ER_DOY_2_5_C_day, k=3, fill=NA, align = "right"),
         ER_DOY_97_5_C = rollmean(ER_DOY_97_5_C_day, k=3, fill=NA, align = "right"),
         NetMetab_DOY_2_5_C = rollmean(NetMetab_DOY_2_5_C_day, k=3, fill=NA, align = "right"),
         NetMetab_DOY_97_5_C = rollmean(NetMetab_DOY_97_5_C_day, k=3, fill=NA, align = "right"),
         .after = doy) %>% 
  mutate(across(c(GPP_DOY_2_5_C, GPP_DOY_97_5_C, GPP_DOY_2_5_C_day, GPP_DOY_97_5_C_day),
                ~ifelse(. < 0, 0, round(.,2)))) %>% 
  mutate(across(c(ER_DOY_2_5_C, ER_DOY_97_5_C, ER_DOY_2_5_C_day, ER_DOY_97_5_C_day), 
                ~ifelse(. > 0, 0, round(.,2)))) %>% 
  ungroup()

```

#### Compare Modeled vs. Historic Quantile Range

Let's see how closely the 2.5% and 97.5% quantile of the multi-year data compares to a specific day's quantile range.

```{r}
Compare<-dt_filtered %>% 
  left_join(dt_2_597_5)  %>%
  select(c(Site, doy, year, `GPP_daily_2.5pct`, `GPP_daily_97.5pct`, 
           `ER_daily_2.5pct`, `ER_daily_97.5pct`, GPP_DOY_2_5_C:ER_DOY_97_5_C)) %>% 
  pivot_longer(names_to = "Measure_Type", values_to = "Value", GPP_daily_2.5pct:ER_DOY_97_5_C) %>% 
  mutate(ER_GPP = if_else(str_detect(Measure_Type, "GPP"), "GPP", "ER"),
         PCT = if_else(str_detect(Measure_Type, "2"), "2_5", "97_5"),
         ER_GPP_PCT = str_c(ER_GPP, PCT, sep = "_")) %>% 
  ungroup()

options<-distinct(Compare, ER_GPP_PCT)

for(i in 1:nrow(options)){
  
  ER_GPP_PCT_i <- as.character(options[i,1])
    
  plot_data_i<-Compare %>% 
    filter(ER_GPP_PCT == ER_GPP_PCT_i) %>% 
    pivot_wider(names_from = "Measure_Type", values_from = "Value")
  
  x<-colnames(plot_data_i)[7]
  y<-colnames(plot_data_i)[8]
  
  plot<-plot_data_i %>%
    filter(Site == "forested") %>% 
    ggplot(aes(x=!!sym(x)*1.25, y=!!sym(y), color=doy, shape = Site)) +
    geom_point(alpha = 0.5) +
    facet_wrap(~year) +
    theme_classic()
  
  print(plot)

}
```

## Final Data

```{r}
Range<- dt_filtered %>% 
  mutate(year = year(date),
         doy = yday(date)) %>% 
  # Merge together datasets
  select(-c(GPP_mean:ER_Rhat, DO_R2_mean:DO_R2_Rhat, K600_daily_mean:errors)) %>% 
  left_join(dt_2_597_5) %>% 
  # Calculate a transmuted (linear) value for each observation
  arrange(Site, date) %>% 
  # Transmute Means
  mutate(across(c(GPP_daily_mean_C, ER_daily_mean_C, Net_Metabolism_C), 
                ~na_interpolation(., option = "linear"), .names = "{col}_Transmuted"),
         .after = Net_Metabolism_C) %>% 
  # Transmute Ranges
  mutate(across(c(GPP_daily_2.5pct,GPP_daily_97.5pct, ER_daily_2.5pct,ER_daily_97.5pct), 
                ~na_interpolation(1.25*., option = "linear"), .names = "{col}_C_Transmuted")) %>%
  # Create mid-point for DOY data
  mutate(GPP_DOY_mid_C = (GPP_DOY_2_5_C + GPP_DOY_97_5_C)/2, 
         ER_DOY_mid_C = (ER_DOY_2_5_C + ER_DOY_97_5_C)/2,
         NetMetab_DOY_mid_C = (NetMetab_DOY_2_5_C + NetMetab_DOY_97_5_C)/2) %>% 
  # Re-arrange
  select(source, Site, date, doy, year, discharge_exceed_1sd, 
         contains("_C"), -contains("5_C_day"), Days_Modeled) %>% 
  select(order(names(.))) %>%   
  # Select Final Number
  mutate(GPP_Daily_NHC_C = if_else(is.na(GPP_daily_mean_C), GPP_DOY_mid_C, GPP_daily_mean_C),
         GPP_2_5_NHC_C = if_else(is.na(GPP_daily_mean_C), GPP_DOY_2_5_C, GPP_daily_2.5pct_C_Transmuted),
         GPP_97_5_NHC_C = if_else(is.na(GPP_daily_mean_C), GPP_DOY_97_5_C, GPP_daily_97.5pct_C_Transmuted),
         ER_Daily_NHC_C = if_else(is.na(ER_daily_mean_C), ER_DOY_mid_C, ER_daily_mean_C),
         ER_2_5_NHC_C = if_else(is.na(ER_daily_mean_C), ER_DOY_2_5_C, ER_daily_2.5pct_C_Transmuted),
         ER_97_5_NHC_C = if_else(is.na(ER_daily_mean_C), ER_DOY_97_5_C, ER_daily_97.5pct_C_Transmuted),
         NetMetab_Daily_NHC_C = if_else(is.na(Net_Metabolism_C), NetMetab_DOY_mid_C, Net_Metabolism_C),
         NetMetab_2_5_NHC_C = if_else(is.na(Net_Metabolism_C), NetMetab_DOY_2_5_C, 
                                      GPP_daily_2.5pct_C_Transmuted + ER_daily_2.5pct_C_Transmuted),
         NetMetab_97_5_NHC_C = if_else(is.na(Net_Metabolism_C), NetMetab_DOY_97_5_C, 
                                       GPP_daily_97.5pct_C_Transmuted + ER_daily_97.5pct_C_Transmuted),
         .after = doy) %>% 
  mutate(GPP_Daily_Final_C = if_else(Site == "forested", GPP_Daily_NHC_C, GPP_daily_mean_C_Transmuted), 
         GPP_2_5_Final_C = if_else(Site == "forested", GPP_2_5_NHC_C, GPP_daily_2.5pct_C_Transmuted), 
         GPP_97_5_Final_C = if_else(Site == "forested", GPP_97_5_NHC_C, GPP_daily_97.5pct_C_Transmuted), 
         ER_Daily_Final_C = if_else(Site == "forested", ER_Daily_NHC_C, ER_daily_mean_C_Transmuted), 
         ER_2_5_Final_C = if_else(Site == "forested", ER_2_5_NHC_C, ER_daily_2.5pct_C_Transmuted), 
         ER_97_5_Final_C = if_else(Site == "forested", ER_97_5_NHC_C, ER_daily_97.5pct_C_Transmuted),
         NetMetab_Daily_Final_C = if_else(Site == "forested", NetMetab_Daily_NHC_C, Net_Metabolism_C_Transmuted), 
         NetMetab_2_5_Final_C = if_else(Site == "forested", NetMetab_2_5_NHC_C, 
                                        GPP_daily_2.5pct_C_Transmuted + ER_daily_2.5pct_C_Transmuted), 
         NetMetab_97_5_Final_C = if_else(Site == "forested", NetMetab_97_5_NHC_C, 
                                         GPP_daily_97.5pct_C_Transmuted + ER_daily_97.5pct_C_Transmuted),
         .after = doy) %>% 
  mutate(Data_Source = if_else(Site == "forested", 
                            if_else(is.na(GPP_daily_mean_C), "Historic Quantile Range", "Model Output"), 
                            if_else(is.na(GPP_daily_mean_C), "Transmuted", "Model Output"))) %>% 
  # Clean-up
  mutate(across(c(GPP_Daily_Final_C, GPP_2_5_Final_C, GPP_97_5_Final_C), ~ifelse(. < 0, 0, .))) %>% 
  mutate(across(c(ER_Daily_Final_C, ER_2_5_Final_C, ER_97_5_Final_C), ~ifelse(. > 0, 0, .))) %>% 
  mutate(across(c(NetMetab_Daily_Final_C, NetMetab_2_5_Final_C, NetMetab_97_5_Final_C), ~ifelse(. > 0, 0, .))) %>% 
  filter(str_detect(year, "2021|2022"))
```

Save the data

```{r}
write.csv(Range, paste0(data_f, "Daily-Metabolism_OUTPUT_MERGED.csv"))
```

Here's a visualization to make it easy to see how the GPP gaps have been filled. 

```{r}
Range %>% 
  filter(date >= start_date & date <= end_date) %>%  
  ggplot(aes(x=date, y=GPP_Daily_Final_C, color = Days_Modeled)) + 
  geom_point() + 
  facet_wrap(~factor(Site,levels=c("forested","wastewater dominated","stormwater dominated")), 
             ncol = 1) + 
  scale_color_manual(values = c("No Model Output" = "red",
                                "GPP/ER Unrealistic" = "green",
                                "Exceeds Discharge Threshold" = "orange",
                                "Passed" = "darkblue")) +
  theme_pubr(legend = "right") + 
  scale_x_date(date_breaks = "2 months",
                 labels = label_date_short(format = c("%Y", "%b", NA, NA)),
                 expand = c(0.005,0.005)) 
```

# Model Inputs 

## Load Input Data

```{r}
# Load in file names
filenames<-list.files(paste0(data_f, "Metabolism_2-2023/data/model_runs/Bayes/mod_and_obs_DO"),
                      pattern="*.csv", full.names = TRUE) 

# Remove NHC
files_to_remove <- grep("NHC", filenames)
filtered_filenames <- filenames[-files_to_remove]

# NHC filenames
NHC_filenames<-list.files(paste0(data_f, "5-6-2023 Run/data/model_runs/Bayes/mod_and_obs_DO"),
                      pattern="*.csv", full.names = TRUE) 

filenames_combined<-c(filtered_filenames, NHC_filenames)
  
# Combine into a list
l <- lapply(filenames_combined, read_csv)

# Clean up names
short_names<-filenames_combined %>%
  str_remove("data/model_runs/Bayes/mod_and_obs_DO/") %>%
  str_remove(data_f) %>% 
  str_remove(".csv")

names(l)<-short_names

# bind into 1 data.table, by columnname, fill missing with NA
inputs <- data.table::rbindlist(l, use.names = TRUE, fill = TRUE, idcol=short_names) %>%
  rename(source=1) %>%
  mutate(Site = if_else(str_detect(source, "NC_NHC"), 'forested',
                    if_else(str_detect(source, 'NC_EllerbeGlenn'), 'wastewater dominated',
                        if_else(str_detect(source, 'NC_EllerbeClub'), 'stormwater dominated',
                                NA_character_))),
         .after=1) %>% 
  group_by(Site, date) %>% 
  mutate(Discharge_Ave = mean(discharge, na.rm = TRUE))
  
```

### Save input data

```{r}
write.csv(inputs, paste0(output_f, "Daily-Metabolism_INPUT_MERGED.csv"))
```

