---
title: "Stream Light Modeling"
author: "Jonny Behrens"
date: "`r Sys.Date()`"
output: html_document
---

# Set-Up 

A walk through: https://psavoy.github.io/StreamLight/articles/2%20Download%20and%20process%20MODIS%20LAI.html. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = '')

#clean out environment
rm(list = ls())

#remotes::install_github('psavoy/StreamLight')
#remotes::install_github('psavoy/StreamLightUtils')
#install.packages('StreamPULSE')
library(pacman)

p_load(StreamPULSE,StreamLight,StreamLightUtils,readr,tidyverse,openxlsx)
```

# PART 1

Use StreamPULSE to ID our sites and format them CORRECTLY

```{r}
NC_sites <- StreamPULSE::query_available_data(region = 'NC')$sites

lat_long<-data.frame(Site_ID = c("EllerbeClub", "EllerbeGlenn", "NHC"),
                     Lat = c(36.0192, 36.0596, 35.9801),
                     Lon = c(-78.8946, -78.8327, -79.0021))

my_sites <- NC_sites %>% 
  dplyr::filter(site %in% c('NHC', 'EllerbeGlenn', 'EllerbeClub')) %>%  
  dplyr::mutate(startDate = as.character('2021-01-01')) %>% 
  dplyr::select(Site_ID = site, startDate) %>% 
  left_join(lat_long) %>% #manually update the lat/long numbers
  data.frame()

```

Create sub-directories 

```{r}
# create a subdirectory for light stuff
light_dir <- 'data/'

if(!dir.exists(light_dir))
  dir.create(light_dir)

# and NLDAS data that we download
NLDAS_dir <- glue::glue(light_dir, 'NLDAS/')

if(!dir.exists(NLDAS_dir))
  dir.create(NLDAS_dir)
```

Bulk download NLDAS data

```{r}
NLDAS_DL_bulk(save_dir = NLDAS_dir,
              site_locs = my_sites,
              startDate = my_sites$startDate)
 
NLDAS_list <- stringr::str_sub(list.files(NLDAS_dir),
                                1, -11)
 
# The following requires you to input the full file name, different for everyone's computer
NLDAS_processed <- StreamLightUtils::NLDAS_proc("data/NLDAS/",
                                                 Site_IDs = NLDAS_list)

# And save it
saveRDS(NLDAS_processed,
         'NLDAS_proc.rds')
```

Create csv that we send to AppEEARS data portal

```{r}
AppEEARS_sites <- my_sites %>% 
  dplyr::select(-startDate)

readr::write_csv(AppEEARS_sites,
                 'data/NLDAS/AppEEARS_sites.csv')

```

Then go to: https://appeears.earthdatacloud.nasa.gov/task/point and make a data request

# PART 2

Unpack the NASA data.

```{r}
Mod_unpack <- AppEEARS_unpack_QC(zip_dir = "data/NLDAS",
                                 zip_file = 'NHC_EC_MODIS.zip',
                                 request_sites = NLDAS_list)

Mod_processed <- AppEEARS_proc(unpacked_LAI = Mod_unpack,
                               fit_method = 'Gu',
                               plot = TRUE)
```

Make driver files

```{r}
driver_sites <- AppEEARS_sites %>% 
  dplyr::mutate(epsg_crs = 4326)

driver_dir <- 'data/driver'
if(!dir.exists(driver_dir))
  dir.create(driver_dir)


driver<-make_driver(site_locs = driver_sites,
            NLDAS_processed = NLDAS_processed,
            MOD_processed = Mod_processed)
#           write_output = TRUE, 
#           save_dir = 'data/driver')

head(driver)

```

## Azimuth

Calculate azimuth for sites. Thanks to Nick Marzolf for this code.

```{r}
p_load(nhdplusTools,geosphere)

points <- driver_sites %>% 
  dplyr::select(Lon, Lat) %>% 
  as.matrix() %>% 
  st_multipoint() %>% 
  st_sfc(crs = 4326) %>% 
  st_cast('POINT')


azimuth_df <- data.frame(Site_ID = character(),
                         azimuth = numeric())
for(k in 1:nrow(driver_sites)){
  site <- driver_sites[k,]
  
  point <- site %>% 
    dplyr::select(Lon, Lat) %>% 
    as.matrix() %>% 
    st_multipoint() %>% 
    st_sfc(crs = 4326) %>% 
    st_cast('POINT')
  
  comid <- discover_nhdplus_id(point)
  
  flowline <- navigate_nldi(list(featureSource = 'comid',
                                 featureID = comid),
                            mode = 'upstreamTributaries',
                            distance_km = 2)
  
  subset <- subset_nhdplus(comids = as.integer(flowline$UT_flowlines$nhdplus_comid[1]),
                           nhdplus_data = 'download',
                           flowline_only = TRUE,
                           return_data = TRUE,
                           overwrite = TRUE)
  
  flow_coords <- st_coordinates(subset$NHDFlowline_Network)
  
  azimuth <- bearing(p1 = flow_coords[1,1:2],
                     p2 = flow_coords[nrow(flow_coords), 1:2])
  
  if(azimuth < 0){azimuth = azimuth + 180}
  
  azimuth_df <- azimuth_df %>% 
    add_row(Site_ID = pull(site, Site_ID),
            azimuth = azimuth)
}
azimuth_df

# Save data
readr::write_csv(azimuth_df,
                 'data/azimuths.csv')
```

Tree height estimates

```{r}
# Function to extract tree height (we need to fix the function)
extract_height_v2<-  function (Site_ID, Lat, Lon, site_crs) 
{
  #Added the "[1]" because there are multiple paths on my computer and that was giving errors
  simard2011 <- raster::raster(paste0(.libPaths()[1], "/StreamLightUtils/data/simard2011.tif")) 
  map_ranges <- raster::setMinMax(simard2011)
  site_location <- data.frame(Lat, Lon)
  if (site_crs == 4326) {
    xy_sf <- sf::st_as_sf(site_location, coords = c("Lon", 
      "Lat"), crs = site_crs)
  }
  else {
    xy_native <- sf::st_as_sf(site_location, coords = c("Lon", 
      "Lat"), crs = site_crs)
    xy_sf <- sf::st_transform(xy_native, crs = 4326)
  }
  suppressWarnings(TH <- raster::extract(map_ranges, xy_sf))
  bound <- setNames(data.frame(Site_ID, Lat, Lon, TH), c("Site_ID", 
    "Lat", "Lon", "TH"))
  return(bound)
}

# Run for all sites
for(i in 1:nrow(driver_sites)){  

  test_i<- extract_height_v2(
    Site_ID = driver_sites[i, "Site_ID"], 
    Lat = driver_sites[i, "Lat"],
    Lon = driver_sites[i, "Lon"],
    site_crs = driver_sites[i, "epsg_crs"])
  
  write.csv(test_i, glue::glue(getwd(), "/data/tree-height_", driver_sites[i,"Site_ID"], ".csv"))
}

```

# PART 3

Start by defining important inputs for the model. 

```{r}
# Define the dataset with all the parameters
# params<-NC_params %>% # this is what is automatically loaded in, we need to change this!
#   mutate(Site_ID = str_replace_all(Site_ID, "NC_", "")) %>%
#   dplyr::filter(str_detect(Site_ID, "NHC"))

# Please verify what overhang should be for ECNG
params<-read.xlsx("data/NHC-ECGS-ECNG_parameters.xlsx") %>% 
  #dplyr::filter(str_detect(Site_ID, "NHC|Glenn")) %>% 
  mutate(Site_ID = str_replace_all(Site_ID, "NC_", "")) 

# Define directories
save_dir<-"output"
read_dir<-"data/driver"
```

Define the function

```{r}
#Function for batching over multiple sites
  batch_model <- function(Site, read_dir, save_dir){
    #Get the model driver
      driver_file <- readRDS(paste(read_dir, "/", Site, "_driver.rds", sep = ""))

    #Get model parameters for the site
      site_p <- params[params[, "Site_ID"] == Site, ]

    #Run the model
      modeled <- stream_light(driver_file, 
        Lat = site_p[, "Lat"], 
        Lon = site_p[, "Lon"],
        channel_azimuth = site_p[, "Azimuth"], 
        bottom_width = site_p[, "Width"], 
        BH = site_p[, "BH"],
        BS = site_p[, "BS"], 
        WL = site_p[, "WL"], 
        TH = site_p[, "TH"], 
        overhang = site_p[, "overhang"],
        overhang_height = site_p[, "overhang_height"], 
        x_LAD = site_p[, "x"]) %>% 
        mutate(Site = Site)

    #Save the output
      saveRDS(modeled, paste(save_dir, "/", Site, "_modeled-on-", Sys.Date(), "_predicted.rds",  sep = ""))

  } #End batch_model 
```

Run the function, save output

```{r}
#Applying the model to all sites
working_dir<-getwd()

#Running the model
lapply(params[, "Site_ID"], 
  FUN = batch_model, 
  read_dir = read_dir,
  save_dir = save_dir) 

# Merge together the output
output_filenames <- list.files(save_dir, pattern="*.rds", full.names = TRUE)
  
Merged_Data<-lapply(output_filenames, readRDS) %>% 
  data.table::rbindlist(use.names = TRUE, fill = TRUE)
  
#Take a look at the output
   head(Merged_Data)
```

Visualize (asimuth really impacts the shape, consider how NHC number is very different from Phil's...)

```{r}
plot_data<-Merged_Data %>% 
  group_by(Site, jday) %>% 
  mutate(PAR_surface_dailyAve = ave(PAR_surface)) 

combo_plot<- plot_data %>% 
  ggplot(aes(x=local_time, y=PAR_surface_dailyAve, color = Site)) +
  geom_point() +
  theme_classic()

combo_plot  
ggsave("output/comboplot_1.jpeg")
```

Save the data

```{r}
write.csv(plot_data, "output/streamLight_estimates.csv")
```


