---
title: "Post-Run Analysis"
author: "Nicholas Marzolf and Jonny Behrens"
date: "`r Sys.Date()`"
knit: (function(inputFile, encoding) {
      out_dir <- "output";
      rmarkdown::render(inputFile, encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
output:
  html_document: 
    theme: cosmo
---

# Set-Up R Environment

```{r setup, echo = FALSE, warning= FALSE, message=FALSE, results='hide'}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

## Set project directory 
projdir <- getwd() # Make sure you have the R Project open! 

## Clear environment
rm(list = ls())

## Libraries
library(pacman)
p_load(tidyverse,dplyr,ggplot2,tidyr,StreamPULSE,dataRetrieval,lubridate,scales,glue,ggpubr,mice)

```

# QA/QC

Evaluate DO Modeled vs. Actual

```{r}
# Dowload Data
filenames <- list.files("data/model_runs/Bayes/mod_and_obs_DO", pattern="*.csv", full.names = TRUE)

l <- lapply(filenames, read_csv)

short_names<-str_remove_all(filenames, "data/model_runs/Bayes/mod_and_obs_DO/|.csv")
names(l)<-short_names

dt <- data.table::rbindlist(l, use.names = TRUE, fill = TRUE, idcol=short_names) %>%
  rename(source=1) %>%
  mutate(Site = if_else(str_detect(source, "NC_NHC"), 'NHC', NA_character_), 
         .after=1) %>% 
  mutate(year = year(date), .after = "date") %>% 
  mutate(month = month(date), .after = "year")

#write.csv(dt, "data/model_runs/Combined-mod_and_obs_DO-Data.csv")
```

```{r}
model_data<-dt %>% 
  na.omit(cols = c("temp.water", "light", "discharge")) %>%
  mutate(cal_day = yday(date)) %>%
  mutate(DO.obs = if_else(DO.obs < 0, NA, DO.obs))

mice_data<-model_data %>% 
  mutate(time = as.numeric(str_remove_all(format(solar.time, format = "%H:%M:%S"),
                                          ":"))) %>% 
  select(DO.obs, temp.water, light, time)
```

## Try out Mice to fill DO gaps

```{r}
dt %>% 
  select(-c(source, depth, DO.sat, date, year)) %>% 
  md.pattern(rotate.names = TRUE)
```

```{r}
mice_data %>% 
  cor(use="pairwise.complete.obs") %>% 
  corrplot::corrplot(method = "color")
```

```{r}
Mice_model_1<-mice(mice_data, method="pmm", m=5)
Mice_model_2<-mice(mice_data, method="norm", m=5)
Mice_model_3<-mice(mice_data, method="rf", m=5)
#Model_4<-na_seadec(mice_data, algorithm = "interpolation", find_frequency = TRUE)
```

```{r}
densityplot(Mice_model_1)
densityplot(Mice_model_2)
densityplot(Mice_model_3)
```

```{r}
summary(Mice_model_1)
summary(Mice_model_2)
summary(Mice_model_3)
```

```{r}
model_data %>%
  select(date, solar.time) %>% 
  bind_cols(complete(Mice_model_1)) %>% 
  filter(date == "2016-10-01") %>% 
  ggplot(aes(x=solar.time, y=DO.obs)) + 
  geom_point() + theme_classic() + 
  labs(title = "What it Should Look Like")

model_data %>%
  select(date, solar.time) %>% 
  bind_cols(complete(Mice_model_1)) %>% 
  filter(date == "2022-08-09") %>% 
  ggplot(aes(x=solar.time, y=DO.obs)) + 
  geom_point() + theme_classic() + 
  labs(title = "Model 1: pmm")

model_data %>%
  select(date, solar.time) %>% 
  bind_cols(complete(Mice_model_2)) %>% 
  filter(date == "2022-08-09") %>% 
  ggplot(aes(x=solar.time, y=DO.obs)) + 
  geom_point() + theme_classic() + 
  labs(title = "Model 2: norm")

model_data %>%
  select(date, solar.time) %>%
  bind_cols(complete(Mice_model_3)) %>%
  filter(date == "2022-08-09") %>%
  ggplot(aes(x=solar.time, y=DO.obs)) +
  geom_point() + theme_classic() +
  labs(title = "Model 3: rf")

```

```{r}
summary(Mice_model_1)

#xyplot(Mice_model_1, DO.obs ~ temp.water + light + discharge, pch=18, cex=1)

densityplot(Mice_model_1)

```

```{r}
imputed_data <- complete(Mice_model_1)

# Assess the convergence of the imputation process
plot(Mice_model_1)

# Compare imputed and observed values for a specific variable (e.g., "variable_name")
compare <- mice::md.pattern(mice_data[, "DO.obs", drop = FALSE], imp = Mice_model_1)
print(compare)

# Assess the imputation quality by calculating RMSE for a specific variable (e.g., "variable_name")
rmse <- mice::postResample(mice_data[, "DO.obs", drop = FALSE], imputed_data[, "DO.obs", drop = FALSE])
print(rmse)

```

## Try out Linear Model

A rough generalized linear model does not look so great. Shown below.

```{r}
linear_model<-glm(`DO.obs` ~ discharge + temp.water + light, 
                  data=na.omit(model_data), family = gaussian)
summary(linear_model)

dt_fit_added<-predict(linear_model, newdata=model_data) %>% 
  as.data.frame() %>% 
  bind_cols(model_data) %>% 
  rename(DO_predicted = 1)

# dt_fit_added %>%
#   ggplot(aes(x= `DO.obs`, y=last_col, color=year)) +
#   geom_point() +
#   facet_wrap(~month) +
#   theme_classic() +
#   labs(x= "Actual DO Value", y="Modeled DO Value", caption="Separated by Month")

```

```{r}
months<-c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12")
  
for(i in 1:length(months)) {                              # Printing ggplot within for-loop

  model_data_i<-model_data %>% 
    
    
    
  plots<-dt_fit_added %>% 
    filter(year == years[i]) %>% 
    ggplot() +
    geom_point(aes(x= solar.time, y=`DO.obs`), color="green") +
    geom_point(aes(x= solar.time, y=DO_predicted), color="yellow") +
    theme_classic() +
    ylab("DO Concentration") + 
    xlab("Day of Year") +
    labs(title = paste(years[i], "Average Daily DO"),
         subtitle = "Green is actual value, yellow is predicted") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") 
  
  print(plots)
}
```

```{r}
years<-c("2016", "2017", "2018", "2019", "2020", "2021", "2022")
  
for(i in 1:length(years)) {                              # Printing ggplot within for-loop

  plots<-dt_fit_added %>% 
    filter(year == years[i]) %>% 
    ggplot() +
    geom_point(aes(x= solar.time, y=`DO.obs`), color="green") +
    geom_point(aes(x= solar.time, y=DO_predicted), color="yellow") +
    theme_classic() +
    ylab("DO Concentration") + 
    xlab("Day of Year") +
    labs(title = paste(years[i], "Average Daily DO"),
         subtitle = "Green is actual value, yellow is predicted") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") 
  
  print(plots)
}
```

## Explore DO

Evaluate the model fits

```{r}
# assign sites
run_sites <- c('NC_NHC_2016-10-01_2017-09-30', 'NC_NHC_2017-10-01_2018-09-30', 
               'NC_NHC_2018-10-01_2019-09-30', 'NC_NHC_2019-10-01_2020-09-30', 
               'NC_NHC_2020-10-01_2021-09-30', 'NC_NHC_2021-10-01_2022-09-30')

# Create an empty table
rating_tbl <- data.frame(
  site = character(),
  year = character(),
  K600_daily_sigma_Rhat = numeric(),
  err_proc_iid_sigma_Rhat = numeric()
)

# Populate table
for(k in 1:length(run_sites)){
  sitecode <- run_sites[1]
  
  daily <- read_csv(glue('data/model_runs/Bayes/daily/{sitecode}_daily.csv'))
  KQ_overall <- read_csv(glue('data/model_runs/Bayes/KQ_overall/{sitecode}_KQ_overall.csv'))
  overall <- read_csv(glue('data/model_runs/Bayes/overall/{sitecode}_overall.csv'))
  
  length = length(daily$GPP_mean)
  GPP_neg <- daily %>% 
    filter(GPP_mean < -0.5) %>% 
    summarise(GPP_imp_per = n()/length) %>% 
    pull()
  
  ER_pos <- daily %>% 
    filter(ER_mean < 0.5) %>% 
    summarise(ER_imp_per = n()/length) %>% 
    pull()
  
  K600_sum <- daily %>% 
    summarise(meanK = mean(K600_daily_mean, na.rm = TRUE),
              minK600 = min(K600_daily_mean, na.rm = TRUE),
              maxK600 = max(K600_daily_mean, na.rm = TRUE)) %>% 
    mutate(rangeK = maxK600 - minK600)
  
  equifin_r2 <- summary(lm(data = daily,
                           ER_mean ~ K600_daily_mean))[8]
  
  rating_tbl <- rating_tbl %>% 
    add_row(
      site = sitecode,
      K600_daily_sigma_Rhat = KQ_overall$K600_daily_sigma_Rhat,
      err_proc_iid_sigma_Rhat = overall$err_proc_iid_sigma_Rhat) %>% 
    mutate(
      RhatL = K600_daily_sigma_Rhat > 1.2 | err_proc_iid_sigma_Rhat > 1.2,
      RhatH = !RhatL,
      KrangeL = K600_sum$rangeK > 50,
      KrangeM = K600_sum$rangeK <= 50 & K600_sum$rangeK > 15,
      KrangeH = K600_sum$rangeK < 15,
      GPP_L = GPP_neg > 50,
      GPP_M = GPP_neg <= 50 & GPP_neg > 25,
      GPP_H = GPP_neg <= 25,
      ER_L = ER_pos > 50,
      ER_M = ER_pos <= 50 & ER_pos > 25,
      ER_H = ER_pos <= 25
      )
}

# View Table
print(rating_tbl)
```

Observed vs. Modeled DO

```{r}
DO<-dt %>% 
  filter(!is.na(DO.obs)) %>% filter(!is.na(DO.mod)) %>% 
  mutate(month = factor(month)) %>% 
  ggscatter(x = "DO.obs", y = "DO.mod", color="month", add = "reg.line") +
  stat_cor() +
  facet_wrap(~year, scales = "free") +
  theme_classic() + 
  scale_color_brewer(palette = "Paired")

DO
```

```{r}
attributes<- c("DO.sat", "depth", "temp.water", "light", "discharge")

for(i in 1:length(attributes)) {  


  plots<-dt %>% 
    filter(!is.na(DO.obs)) %>% filter(!is.na(DO.mod)) %>% 
    filter(year > 2020) %>% filter(year < 2023) %>% 
    mutate(month = factor(month)) %>% 
    ggplot() +
    geom_point(aes(x=date, y=DO.obs), colour = "blue") +
    geom_point(aes(x=date, y=!!sym(attributes[i]), color = "gray")) +
    facet_wrap(~year, ncol=1, scales = "free") +
    theme_classic() + 
    labs(title = paste0(attributes[i], " vs. Q"))
  
  print(plots)
}

```

# Explore missing data

First Run

```{r}
# load streampulse data
StreamPULSE_Data_raw<-readRDS("data/prep/NC_NHC_prep.rds")

StreamPULSE_Data<-StreamPULSE_Data_raw$data  %>% 
  unclass() %>% as.data.frame() %>%
  mutate(date = as.Date(`solar.time`)) %>% 
  select(-solar.time) %>% 
  mutate(Site = "NHC") %>% 
  group_by(date, Site) %>% 
  summarise_all(mean)

# Dowload Daily data from first run 
filenames <- list.files("C:/Users/jbehr/OneDrive - Duke University/Documents/0. Research/0 Ellerbe Creek/R/_Metab_Explore/Metabolism_2-2023/data/model_runs/Bayes/daily", pattern="*.csv", full.names = TRUE)
l <- lapply(filenames, read_csv)

short_names<-str_remove_all(filenames, "C:/Users/jbehr/OneDrive - Duke University/Documents/0. Research/0 Ellerbe Creek/R/_Metab_Explore/Metabolism_2-2023/data/model_runs/Bayes/daily/|.csv")
names(l)<-short_names

daily_data <- data.table::rbindlist(l, use.names = TRUE, fill = TRUE, idcol=short_names) %>%
  rename(source = 1) %>% 
  mutate(Site = if_else(str_detect(source, "NC_NHC"), 'NHC', NA_character_), .after=1) %>% 
  mutate(year = year(date), .after = "date") %>% 
  mutate(month = month(date), .after = "year") %>% 
  mutate(Run = 1, .after=1)


```

Second Run

```{r}
#discharge data
daily_Q_data<-read.csv("data/model_runs/Bayes/combined/datadaily_combined.csv") %>% 
  mutate(date = as.Date(date, try.formats = c("%Y-%m-%d"))) %>%
  mutate(Site = "NHC", .after=1) %>% 
  mutate(year = year(date), .after = "date") %>% 
  mutate(month = month(date), .after = "year") %>% 
  mutate(Run = 3, .after=1)

# Dowload Daily data
daily_data2<-read.csv("data/model_runs/Bayes/combined/daily_combined.csv") %>% 
  mutate(date = as.Date(date, try.formats = c("%Y-%m-%d"))) %>%
  mutate(Site = "NHC", .after=1) %>% 
  mutate(year = year(date), .after = "date") %>% 
  mutate(month = month(date), .after = "year") %>% 
  filter(date <= "2023-01-09") %>% 
  mutate(Run = 3, .after=1)
```

Let's look at how many missing days are missing estimates.

```{r}
some_information<-daily_data %>% 
  filter(Site == "NHC") %>% 
  mutate(GPP_ER_Missing = if_else(is.na(GPP_mean) & is.na(ER_mean), "2", 
                              if_else(is.na(GPP_mean) & !is.na(ER_mean), "1-GPP",
                                  if_else(!is.na(GPP_mean) & is.na(ER_mean), "1-ER",
                                      if_else(!is.na(GPP_mean) & !is.na(ER_mean), "0", NA_character_)))))
some_information %>% 
  group_by(GPP_ER_Missing) %>% count()

some_information2<-daily_data2 %>% 
  filter(Site == "NHC") %>% 
  mutate(GPP_ER_Missing = if_else(is.na(GPP_mean) & is.na(ER_mean), "2", 
                              if_else(is.na(GPP_mean) & !is.na(ER_mean), "1-GPP",
                                  if_else(!is.na(GPP_mean) & is.na(ER_mean), "1-ER",
                                      if_else(!is.na(GPP_mean) & !is.na(ER_mean), "0", NA_character_)))))
some_information2 %>% 
  group_by(GPP_ER_Missing) %>% count()
```

Let's look at Rhat differences

```{r}
rHats<-c("GPP_Rhat", "ER_daily_Rhat", "K600_daily_Rhat")
means<-c("GPP_mean", "ER_mean", "ER_mean")

merged2<-daily_data %>%
  full_join(daily_data2) %>% 
  left_join(StreamPULSE_Data) %>% 
  left_join(select(daily_Q_data, c(Site, date, discharge.daily)))

for(i in 1:length(rHats)) {  

  plots<-merged2 %>% 
    filter(!is.na(means[i])) %>% 
    ggplot(aes(x=!!sym(rHats[i]), y=as.character(Run), fill=as.character(Run), color = as.character(Run))) + 
    ggridges::geom_density_ridges(alpha = 0.5) +
    theme_classic() + 
    labs(x= paste0(rHats[i]), y="Density (Categorized by Run Number)") + 
    theme(legend.position = "none")
  
  print(plots)
}

```

```{r}
missing_modeled_wide<-merged2 %>% 
  filter(Run == 1) %>% 
  filter(is.na(GPP_mean) & !is.na(Site) & !is.na(year)) %>% 
  mutate(DO_status = if_else(is.na(DO.obs), "Missing DO", "Has DO")) %>% 
  select(Run:date, DO_status, `DO.obs`:`discharge.daily`) 

missing_modeled<-missing_modeled_wide %>% 
  pivot_longer(names_to = "measure", values_to = "value", 5:11) 
  
t0<-missing_modeled_wide %>% 
  group_by(DO_status) %>% count()

t1<-missing_modeled %>% 
  filter(is.na(value)) %>% 
  group_by(measure, DO_status) %>% 
  count()

t2<-missing_modeled %>% 
  filter(!is.na(value)) %>% 
  group_by(measure, DO_status) %>% 
  count()

t3<-merged2 %>% 
  mutate(DO_status = if_else(is.na(DO.obs), "Missing DO", "Has DO")) %>% 
  filter(is.na(GPP_mean) & !is.na(Site) & !is.na(year)) %>%
  filter(!is.na(DO.obs)) %>% 
  select(Run:date, DO_status, `DO.obs`:`discharge.daily`) %>% 
  pivot_longer(names_to = "measure", values_to = "value", 5:11) %>%  
  filter(is.na(value)) %>% 
  group_by(measure, DO_status) %>% 
  count()

pander::pander(t0,caption="^ Which have DO")
pander::pander(t1,caption="^ Count of values that are NA (bad data)")
pander::pander(t2,caption="^ Count of values that ARE NOT NA (good data)")
pander::pander(t3,caption="^ Count where DO isn't missing")

```

# Explore annual data

```{r}
GPP_day_summary<-daily_data2 %>% 
  mutate(day = yday(date)) %>%
  mutate(GPP_mean = if_else(GPP_mean <= 0, NA, GPP_mean)) %>% 
  group_by(day) %>% 
  summarise(min = min(GPP_mean, na.rm = TRUE), 
            max = max(GPP_mean, na.rm = TRUE),
            sd = sd(GPP_mean, na.rm = TRUE),
            mean = mean(GPP_mean, na.rm = TRUE),
            q1 = quantile(GPP_mean, 0.25, na.rm = TRUE),
            q3 = quantile(GPP_mean, 0.75, na.rm = TRUE),
            n = sum(!is.na(GPP_mean)))

ER_day_summary<-daily_data2 %>% 
  mutate(day = yday(date)) %>%
  mutate(ER_mean = if_else(ER_mean >= 0, NA, ER_mean)) %>% 
  group_by(day) %>% 
  summarise(min = min(ER_mean, na.rm = TRUE), 
            max = max(ER_mean, na.rm = TRUE),
            sd = sd(ER_mean, na.rm = TRUE),
            mean = mean(ER_mean, na.rm = TRUE),
            q1 = quantile(ER_mean, 0.25, na.rm = TRUE),
            q3 = quantile(ER_mean, 0.75, na.rm = TRUE),
            n = sum(!is.na(ER_mean)))
```

```{r}
GPP_day_summary %>% group_by(n) %>% count()

ER_day_summary %>% group_by(n) %>% count()

```

```{r}
# GPP
years<-c("2016", "2017", "2018", "2019", "2020", "2021", "2022")
  
for(i in 1:length(years)) {                              # Printing ggplot within for-loop

  plots<-daily_data2 %>% 
    mutate(day = yday(date)) %>%
    mutate(GPP_mean = if_else(GPP_mean <= 0, NA, GPP_mean)) %>%
    filter(year == years[i]) %>% 
    ggplot() +
    geom_point(aes(x= day, y = GPP_mean), color="green") +
    geom_ribbon(data= GPP_day_summary, aes(x= day, ymin = min, ymax = max), 
                alpha = 0.2, fill="blue") +
    theme_classic() +
    ylab(paste(years[i])) + 
    xlab("Day of Year") +
    labs(title = paste(years[i], "Daily GPP"),
         subtitle = "Blue is the average value, for a given calendar day, across all years of data") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") 
  
  print(plots)
}
```

# Explore GLMs for GPP

```{r}
Inputs_Daily_Values<-dt %>% 
  na.omit(cols = c("temp.water", "light", "discharge")) %>%
  group_by(date) %>% 
  mutate(T_ave = ave(temp.water),
         Q_ave = ave(discharge),
         Q_max = max(discharge),
         light_ave = ave(light),
         light_max = max(light)) %>% 
  select(date, T_ave:light_max) %>% 
  distinct(date, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(day_of_year = yday(date))

GPP_ER_Model_Data<-daily_data2 %>% 
  select(date, GPP_mean, ER_mean, GPP_daily_mean, ER_daily_mean) %>% 
  full_join(Inputs_Daily_Values) %>% 
  filter(!is.na(T_ave)) %>% 
  mutate(GPP_daily_mean = if_else(GPP_daily_mean < 0, NA, GPP_daily_mean)) %>% 
  mutate(ER_daily_mean = if_else(ER_daily_mean > 0, NA, ER_daily_mean))

```

## T ave, Q ave, L ave

```{r}
glm_1<-glm(GPP_daily_mean ~ T_ave + Q_ave + light_ave + day_of_year, data=na.omit(GPP_ER_Model_Data), family = gaussian)
summary(glm_1)

predict_1<-predict(glm_1, newdata=GPP_ER_Model_Data) 
GPP_ER_Model_Data$GPPdailymean_TaQaLa<-predict_1
```

## T ave, Q ave, light max

```{r}
glm_2<-glm(GPP_daily_mean ~ T_ave + Q_ave + light_max + day_of_year, data=na.omit(GPP_ER_Model_Data), family = gaussian)
summary(glm_2)

predict_2<-predict(glm_2, newdata=GPP_ER_Model_Data) 
GPP_ER_Model_Data$GPPdailymean_TaQaLm<-predict_2
```

## T ave, L ave, Q max

```{r}
glm_3<-glm(GPP_daily_mean ~ T_ave + Q_max + light_ave + day_of_year, data=na.omit(GPP_ER_Model_Data), family = gaussian)
summary(glm_3)

predict_3<-predict(glm_3, newdata=GPP_ER_Model_Data) 
GPP_ER_Model_Data$GPPdailymean_TaQmLa<-predict_3
```

## T ave, L max, Q max

```{r}
glm_4<-glm(GPP_daily_mean ~ T_ave + Q_max + light_max + day_of_year, data=na.omit(GPP_ER_Model_Data), family = gaussian)
summary(glm_4)

predict_4<-predict(glm_4, newdata=GPP_ER_Model_Data) 
GPP_ER_Model_Data$GPPdailymean_TaQmLm<-predict_4
```

```{r}
years<-c("2016", "2017", "2018", "2019", "2020", "2021", "2022")

time_seq<-seq(as.Date("2016-10-01"), as.Date("2022-09-29"), by="1 day") %>% 
  as.data.frame() %>% 
  rename(date = 1)
  
for(i in 1:length(years)) {                              # Printing ggplot within for-loop

  plots<-GPP_ER_Model_Data %>% 
    full_join(time_seq) %>% 
    mutate(year = year(date)) %>% 
    filter(year == years[i]) %>% 
    ggplot() +
    geom_point(aes(x= date, y=GPP_daily_mean), color="green") +
    geom_line(aes(x=date, y=GPPdailymean_TaQaLa), color = "blue", na.rm = TRUE) + 
    geom_line(aes(x=date, y=GPPdailymean_TaQaLm), color = "orange", na.rm = TRUE) + 
    geom_line(aes(x=date, y=GPPdailymean_TaQmLa), color = "purple", na.rm = TRUE) + 
    geom_line(aes(x=date, y=GPPdailymean_TaQmLm), color = "red", na.rm = TRUE) + 
    theme_classic() +
    ylab("GPP Daily Mean") + 
    xlab("Day of Year") +
    labs(title = paste(years[i], "Predicting GPP"),
         subtitle = "Green is actual value, other colors are different GLMs") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") 
  
  print(plots)
}
```

```{r}
# ER
years<-c("2016", "2017", "2018", "2019", "2020", "2021", "2022")
  
for(i in 1:length(years)) {                              # Printing ggplot within for-loop

  plots<-daily_data2 %>% 
    mutate(day = yday(date)) %>%
    mutate(ER_mean = if_else(ER_mean >= 0, NA, ER_mean)) %>%
    filter(year == years[i]) %>% 
    ggplot() +
    geom_point(aes(x= day, y = ER_mean), color="brown") +
    geom_ribbon(data= ER_day_summary, aes(x= day, ymin = min, ymax = max), 
                alpha = 0.2, fill="blue") +
    theme_classic() +
    ylab(paste(years[i])) + 
    xlab("Day of Year") +
    labs(title = paste(years[i], "Daily ER"),
         subtitle = "Blue is the range of values, for a given calendar day, across all years of data") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom") 
  
  print(plots)
}
```

# Visualize

## Prep Data

```{r}
# # assign sites
# run_sites <- c('NC_NHC')
# 
# filenames <- list.files("data/model_runs/Bayes/daily", pattern="*.csv", full.names = TRUE)
# 
# l <- lapply(filenames, read_csv)
# 
# short_names<-filenames %>%
#   str_remove("data/model_runs/Bayes/daily/") %>%
#   str_remove(".csv")
# 
# names(l)<-short_names
# 
# #bind l together to one larger data.table, by columnname, fill missing with NA
# dt <- data.table::rbindlist( l, use.names = TRUE, fill = TRUE, idcol=short_names) %>%
#   rename(source=1) %>%
#   mutate(Site = if_else(str_detect(source, "NC_NHC"), 'NHC', NA_character_),
#          .after=1)
# 
# write.csv(dt, "data/model_runs/Combined-Daily-Data.csv")
```

# Download Data

```{r}
data_raw<-read_csv("data/model_runs/Bayes/combined/daily_combined.csv") %>% 
  mutate(year = year(date), .after = date)

plot_data<-data_raw %>% 
  filter(date < "2022-04-10") %>% # only looking at 2021
  filter(date > "2021-04-10") %>% 
 # group_by(Site) %>% 
  filter(!is.na(GPP_mean)) %>% 
  mutate(cumGPP = cumsum(GPP_mean),
         cumER = -1*(cumsum(-1*ER_mean)))
```

# QA/QC

Count of days with no data

```{r}
missing_days<-data_raw %>% 
  group_by(year, valid_day) %>%
  count() %>% 
  ggplot(aes(x="", y=n, fill=valid_day)) +
  geom_col() + 
  geom_text(aes(label = n), position = position_stack(vjust=0.5)) +
  facet_wrap(~year) +
  coord_polar(theta = "y") + 
  theme_void() + labs(title = "Days with Data")

missing_days
```

# Plot Data

## Cumulative Plots

```{r}
NHC_metab<-plot_data %>% 
  #filter(Site %in% c('NHC')) %>%
  ggplot(., aes(x = as.Date(date))) +
  geom_area(aes(y = cumGPP, fill = "GPP"))+
  geom_area(aes(y = cumER, fill = "ER"))+
  ylim(-2000, 500) + 
  theme_classic() +
  scale_fill_manual(name = element_blank(),
                   values = alpha(c('#C76C05', "#208D01"), 0.8)) + 
  scale_x_date(date_breaks = "1 month",
                 labels = label_date_short(format = c("%Y", "%b", NA, NA)),
                 expand = c(0.005,0.005)) +
  labs(x=element_blank(), y=element_blank(), title = "NHC") +
  theme(text = element_text(size = 20))

NHC_metab
ggsave("output/NHC_metab.png", width= 10, height= 6)

```

## Point Plots

```{r}
NHC_metab_p<-plot_data %>% 
  #filter(Site %in% c('NHC')) %>%
  filter(valid_day == "TRUE") %>% 
  filter(GPP_daily_mean >= 0) %>% filter(ER_daily_mean <= 0) %>% 
  ggplot(., aes(x = as.Date(date))) +
  geom_point(aes(y = GPP_daily_mean, color = "GPP"))+
  geom_ribbon(aes(ymin= `GPP_daily_2.5pct`, ymax= `GPP_daily_97.5pct`, fill = "GPP"))+
  geom_point(aes(y = ER_daily_mean, color = "ER"))+
  geom_ribbon(aes(ymin= `ER_daily_2.5pct`, ymax= `ER_daily_97.5pct`, fill = "ER"))+
  ylim(-25, 5) + 
  theme_classic() +
  scale_color_manual(name = element_blank(),
                   values = alpha(c('#C76C05', "#208D01"), 0.8)) + 
  scale_fill_manual(name = element_blank(),
                   values = alpha(c('#C76C05', "#208D01"), 0.3)) + 
  scale_x_date(date_breaks = "1 month",
                 labels = label_date_short(format = c("%Y", "%b", NA, NA)),
                 expand = c(0.005,0.005)) +
  labs(x=element_blank(), y=element_blank(), title = "NHC") +
  theme(text = element_text(size = 20))

NHC_metab_p
ggsave("output/NHC_metabv2.png", width= 10, height= 6)

```

# Visualize

## Prep Data

```{r}
# # assign sites
# run_sites <- c('NC_NHC')
# 
# filenames <- list.files("data/model_runs/Bayes/daily", pattern="*.csv", full.names = TRUE)
# 
# l <- lapply(filenames, read_csv)
# 
# short_names<-filenames %>%
#   str_remove("data/model_runs/Bayes/daily/") %>%
#   str_remove(".csv")
# 
# names(l)<-short_names
# 
# #bind l together to one larger data.table, by columnname, fill missing with NA
# dt <- data.table::rbindlist( l, use.names = TRUE, fill = TRUE, idcol=short_names) %>%
#   rename(source=1) %>%
#   mutate(Site = if_else(str_detect(source, "NC_NHC"), 'NHC', NA_character_),
#          .after=1)
# 
# write.csv(dt, "data/model_runs/Combined-Daily-Data.csv")
```
