---
title: "Post-Run Analysis"
author: "Jonny Behrens and Nicholas Marzolf"
date: "`r Sys.Date()`"
knit: (function(inputFile, encoding) {
      out_dir <- "output";
      rmarkdown::render(inputFile, encoding=encoding,
                        output_dir=file.path(dirname(inputFile), out_dir))})
output:
  html_document: 
    theme: cosmo
---

# Set-Up R Environment

```{r setup, echo = FALSE, warning= FALSE, message=FALSE, results='hide'}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

## Set project directory 
projdir <- getwd() # Make sure you have the R Project open! 

## Clear environment
rm(list = ls())

## Libraries
library(pacman)
p_load(tidyverse,StreamPULSE,dataRetrieval,lubridate,scales,glue,ggpubr,ggridges,knitr)
```

# Merge together yearly data into a combined folder for Bayes

The following code will give an error if it has already been run and the files already are created!

```{r}
Bayes_data_folder<-"data/model_runs/Bayes/"
# get a list of all subfolders in the parent folder
subfolders <- c("daily", "datadaily", "estimates")

# create directory
combined_dir <- 'data/model_runs/Bayes/combined/'
dir.create(combined_dir)
    
# loop through each subfolder
for (i in 1:length(subfolders)) {

  # subfolder name
  subfolder_name<-paste0(Bayes_data_folder, subfolders[i])
  
  # get a list of all CSV files in the subfolder
  csv_files <- list.files(subfolder_name, pattern = ".csv")

  # loop through each CSV file and read it into a dataframe
  dfs <- list()
  for (j in 1:length(csv_files)) {
    df <- read.csv(paste0(subfolder_name, "/", csv_files[j]))
    dfs[[j]] <- df }

  # combine all dataframes into a single dataframe
  combined_df <- dplyr::bind_rows(dfs)

  # create a unique filename for the output CSV file
  output_file <- paste0(str_remove_all(subfolder_name, Bayes_data_folder), "_combined", ".csv")

  # set the working directory back to the parent folder
 # setwd("..")

  # write the combined dataframe to a new CSV file in the subfolder
  write.csv(combined_df, file = paste0(Bayes_data_folder, "combined/", output_file), row.names = FALSE)

}
```

# QA/QC

Evaluate the model fits

```{r}
# assign sites
run_sites <- c('NC_NHC_2020-10-01_2021-09-30', 'NC_NHC_2021-10-01_2022-09-30', 'NC_NHC_2022-10-01_2023-03-20')

# Create an empty table
rating_tbl <- data.frame(
  site = character(),
  year = character(),
  K600_daily_sigma_Rhat = numeric(),
  err_proc_iid_sigma_Rhat = numeric()
)

# Populate table
for(k in 1:length(run_sites)){
  sitecode <- run_sites[k]
  
  daily <- read_csv(glue('data/model_runs/Bayes/daily/{sitecode}_daily.csv'))
  KQ_overall <- read_csv(glue('data/model_runs/Bayes/KQ_overall/{sitecode}_KQ_overall.csv'))
  overall <- read_csv(glue('data/model_runs/Bayes/overall/{sitecode}_overall.csv'))
  
  length = length(daily$GPP_mean)
  GPP_neg <- daily %>% 
    filter(GPP_mean < -0.5) %>% 
    summarise(GPP_imp_per = n()/length) %>% 
    pull()
  
  ER_pos <- daily %>% 
    filter(ER_mean < 0.5) %>% 
    summarise(ER_imp_per = n()/length) %>% 
    pull()
  
  K600_sum <- daily %>% 
    summarise(meanK = mean(K600_daily_mean, na.rm = TRUE),
              minK600 = min(K600_daily_mean, na.rm = TRUE),
              maxK600 = max(K600_daily_mean, na.rm = TRUE)) %>% 
    mutate(rangeK = maxK600 - minK600)
  
  equifin_r2 <- summary(lm(data = daily,
                           ER_mean ~ K600_daily_mean))[8]
  
  rating_tbl <- rating_tbl %>% 
    add_row(
      site = sitecode,
      K600_daily_sigma_Rhat = KQ_overall$K600_daily_sigma_Rhat,
      err_proc_iid_sigma_Rhat = overall$err_proc_iid_sigma_Rhat) %>% 
    mutate(
      RhatL = K600_daily_sigma_Rhat > 1.2 | err_proc_iid_sigma_Rhat > 1.2,
      RhatH = !RhatL,
      KrangeL = K600_sum$rangeK > 50,
      KrangeM = K600_sum$rangeK <= 50 & K600_sum$rangeK > 15,
      KrangeH = K600_sum$rangeK < 15,
      GPP_L = GPP_neg > 50,
      GPP_M = GPP_neg <= 50 & GPP_neg > 25,
      GPP_H = GPP_neg <= 25,
      ER_L = ER_pos > 50,
      ER_M = ER_pos <= 50 & ER_pos > 25,
      ER_H = ER_pos <= 25
      )
}

# View Table
print(rating_tbl)
```

#Evaluate DO Modeled vs. Actual

```{r}
# Download Data
dt <- read.csv("data/model_runs/Bayes/combined/mod_and_obs_DO_combined.csv") %>%
  mutate(date = as.Date(date, try.formats = c("%Y-%m-%d"))) %>%
  mutate(solar.time = ymd_hms(solar.time)) %>% 
  mutate(Site = 'NHC') %>% 
  mutate(year = year(date), .after = "date") %>% 
  mutate(month = month(date), .after = "year")
```

## Model

A rough linear model does not look so great. Shown below.

```{r}
# model<-lm(`DO.obs` ~ depth + temp.water + light + discharge, data=na.omit(dt))
# 
# summary(model)
# 
# dt_fit_added<-dt %>% 
#   na.omit() %>% 
#   bind_cols(model$fitted.values) %>% 
#   rename(last_col = 14)
# 
# dt_fit_added %>% 
#   ggplot(aes(x= `DO.obs`, y=last_col, color=year)) +
#   geom_point() +
#   facet_wrap(~month) +
#   theme_classic() + 
#   labs(x= "Actual DO Value", y="Modeled DO Value", caption="Separated by Month")
  
```


## Explore DO 

Observed vs. Modeled DO

```{r}
# DO<-dt %>% 
#   filter(!is.na(DO.obs)) %>% filter(!is.na(DO.mod)) %>% 
#   mutate(month = factor(month)) %>% 
#   ggscatter(x = "DO.obs", y = "DO.mod", color="month", add = "reg.line") +
#   stat_cor() +
#   facet_wrap(~year, scales = "free") +
#   theme_classic() + 
#   scale_color_brewer(palette = "Paired")
# 
# DO
```

```{r}
# DO_Q<-dt %>% 
#   filter(!is.na(DO.obs)) %>% filter(!is.na(DO.mod)) %>% 
#   filter(year > 2020) %>% filter(year < 2023) %>% 
#   mutate(month = factor(month)) %>% 
#   ggplot() +
#   geom_point(aes(x=date, y=DO.mod), colour = "blue") +
#   geom_point(aes(x=date, y=discharge, color = "gray")) +
#   facet_wrap(~year, ncol=1, scales = "free") +
#   theme_classic() + labs(title = "DO vs. Q")
# 
# DO_depth<-dt %>% 
#   filter(!is.na(DO.obs)) %>% filter(!is.na(DO.mod)) %>% 
#   filter(year > 2020) %>% filter(year < 2023) %>% 
#   mutate(month = factor(month)) %>% 
#   ggplot() +
#   geom_point(aes(x=date, y=DO.mod), colour = "blue") +
#   geom_point(aes(x=date, y=depth, color = "black")) +
#   facet_wrap(~year, ncol=1, scales = "free") +
#   theme_classic()+ labs(title = "DO vs. Depth")
# 
# DO_temp<-dt %>% 
#   filter(!is.na(DO.obs)) %>% filter(!is.na(DO.mod)) %>% 
#   filter(year > 2020) %>% filter(year < 2023) %>% 
#   mutate(month = factor(month)) %>% 
#   ggplot() +
#   geom_point(aes(x=date, y=DO.mod), colour = "blue") +
#   geom_point(aes(x=date, y=temp.water, color = "green")) +
#   facet_wrap(~year, ncol=1, scales = "free") +
#   theme_classic() + labs(title = "DO vs. temp")
# 
# DO_light<-dt %>% 
#   filter(!is.na(DO.obs)) %>% filter(!is.na(DO.mod)) %>% 
#   filter(year > 2020) %>% filter(year < 2023) %>% 
#   mutate(month = factor(month)) %>% 
#   ggplot() +
#   geom_point(aes(x=date, y=DO.mod), colour = "blue") +
#   geom_point(aes(x=date, y=light), colour = "orange") +
#   facet_wrap(~year, ncol=1, scales = "free") +
#   theme_classic() + labs(title = "DO vs. light")
# 
# DO_Q
# DO_depth
# DO_temp
# DO_light
```

# Explore missing data

First Run 

```{r}
# load streampulse data
StreamPULSE_Data_raw<-readRDS("data/prep/NC_NHC_prep.rds")

StreamPULSE_Data<-StreamPULSE_Data_raw$data  %>% 
  unclass() %>% as.data.frame() %>%
  mutate(date = as.Date(`solar.time`)) %>% 
  select(-solar.time) %>% 
  mutate(Site = "NHC") %>% 
  group_by(date, Site) %>% 
  summarise_all(mean)

# Dowload Daily data from first run 
filenames <- list.files("C:/Users/jrb146/OneDrive - Duke University/Documents/0. Research/0 Ellerbe Creek/R/_Metab_Explore/Metabolism_2-2023/data/model_runs/Bayes/daily", pattern="*.csv", full.names = TRUE)
l <- lapply(filenames, read_csv)

short_names<-str_remove_all(filenames, "C:/Users/jrb146/OneDrive - Duke University/Documents/0. Research/0 Ellerbe Creek/R/_Metab_Explore/Metabolism_2-2023/data/model_runs/Bayes/daily/|.csv")
names(l)<-short_names

daily_data <- data.table::rbindlist(l, use.names = TRUE, fill = TRUE, idcol=short_names) %>%
  rename(source = 1) %>% 
  mutate(Site = if_else(str_detect(source, "NC_NHC"), 'NHC', NA_character_), .after=1) %>% 
  mutate(year = year(date), .after = "date") %>% 
  mutate(month = month(date), .after = "year") %>% 
  mutate(Run = 1, .after=1)


```

Second Run 

```{r}
#discharge data
daily_Q_data<-read.csv("data/model_runs/Bayes/combined/datadaily_combined.csv") %>% 
  mutate(date = as.Date(date, try.formats = c("%Y-%m-%d"))) %>%
  mutate(Site = "NHC", .after=1) %>% 
  mutate(year = year(date), .after = "date") %>% 
  mutate(month = month(date), .after = "year") %>% 
  mutate(Run = 2, .after=1)

# Dowload Daily data
daily_data2<-read.csv("data/model_runs/Bayes/combined/daily_combined.csv") %>% 
  mutate(date = as.Date(date, try.formats = c("%Y-%m-%d"))) %>%
  mutate(Site = "NHC", .after=1) %>% 
  mutate(year = year(date), .after = "date") %>% 
  mutate(month = month(date), .after = "year") %>% 
  filter(date <= "2023-01-09") %>% 
  mutate(Run = 2, .after=1)
```

Let's look at how many missing days are missing estimates.

```{r}
some_information<-daily_data %>% 
  filter(Site == "NHC") %>% 
  mutate(GPP_ER_Missing = if_else(is.na(GPP_mean) & is.na(ER_mean), "2", 
                              if_else(is.na(GPP_mean) & !is.na(ER_mean), "1-GPP",
                                  if_else(!is.na(GPP_mean) & is.na(ER_mean), "1-ER",
                                      if_else(!is.na(GPP_mean) & !is.na(ER_mean), "0", NA_character_)))))
some_information %>% 
  group_by(GPP_ER_Missing) %>% count()

some_information2<-daily_data2 %>% 
  filter(Site == "NHC") %>% 
  mutate(GPP_ER_Missing = if_else(is.na(GPP_mean) & is.na(ER_mean), "2", 
                              if_else(is.na(GPP_mean) & !is.na(ER_mean), "1-GPP",
                                  if_else(!is.na(GPP_mean) & is.na(ER_mean), "1-ER",
                                      if_else(!is.na(GPP_mean) & !is.na(ER_mean), "0", NA_character_)))))
some_information2 %>% 
  group_by(GPP_ER_Missing) %>% count()
```

Let's look at Rhat differences

```{r}
# merged<-daily_data %>% 
#   full_join(daily_data2)
merged2<-daily_data %>%
  full_join(daily_data2) %>% 
  left_join(StreamPULSE_Data) %>% 
  left_join(select(daily_Q_data, c(Site, date, discharge.daily)))
  
Rhat_GPP<-merged2 %>%
  filter(!is.na(GPP_mean)) %>% 
  ggplot(aes(x=GPP_Rhat, y=as.character(Run), fill=as.character(Run), color = as.character(Run))) + #update based on your data
  geom_density_ridges(alpha = 0.5) +
  theme_classic()

Rhat_GPP

Rhat_ER<-merged2 %>%
  filter(!is.na(ER_mean)) %>% 
  ggplot(aes(x=ER_Rhat, y=as.character(Run), fill=as.character(Run), color = as.character(Run))) + #update based on your data
  geom_density_ridges(alpha = 0.5) +
  theme_classic()

Rhat_ER

K600_daily_Rhat<-merged2 %>%
  filter(!is.na(ER_mean)) %>% 
  ggplot(aes(x=K600_daily_Rhat, y=as.character(Run), fill=as.character(Run), color = as.character(Run))) + #update based on your data
  geom_density_ridges(alpha = 0.5) +
  theme_classic()

K600_daily_Rhat
```

```{r}
missing_modeled_wide<-merged2 %>% 
  filter(Run == 1) %>% 
  filter(is.na(GPP_mean) & !is.na(Site) & !is.na(year)) %>% 
  mutate(DO_status = if_else(is.na(DO.obs), "Missing DO", "Has DO")) %>% 
  select(Run:date, DO_status, `DO.obs`:`discharge.daily`) 

missing_modeled<-missing_modeled_wide %>% 
  pivot_longer(names_to = "measure", values_to = "value", 5:11) 
  
t0<-missing_modeled_wide %>% 
  group_by(DO_status) %>% count()

t1<-missing_modeled %>% 
  filter(is.na(value)) %>% 
  group_by(measure, DO_status) %>% 
  count()

t2<-missing_modeled %>% 
  filter(!is.na(value)) %>% 
  group_by(measure, DO_status) %>% 
  count()

t3<-merged2 %>% 
  mutate(DO_status = if_else(is.na(DO.obs), "Missing DO", "Has DO")) %>% 
  filter(is.na(GPP_mean) & !is.na(Site) & !is.na(year)) %>%
  filter(!is.na(DO.obs)) %>% 
  select(Run:date, DO_status, `DO.obs`:`discharge.daily`) %>% 
  pivot_longer(names_to = "measure", values_to = "value", 5:11) %>%  
  filter(is.na(value)) %>% 
  group_by(measure, DO_status) %>% 
  count()

pander::pander(t0,caption="^ Which have DO")
pander::pander(t1,caption="^ Count of values that are NA (bad data)")
pander::pander(t2,caption="^ Count of values that ARE NOT NA (good data)")
pander::pander(t3,caption="^ Count where DO isn't missing")

```

## Let's look at missing data

Merge together annotated data

```{r}
# Download Annotated data
annotated<-read.csv("data/model_runs/Bayes/combined/datadaily_annotated_combined.csv") %>% 
  mutate(date = as.Date(date, tryFormats = "%m/%d/%Y")) %>%
  mutate(Site = "NHC", .after=1) %>% 
  mutate(year = year(date), .after = "date") %>% 
  mutate(month = month(date), .after = "year") %>% 
  mutate(Run = 2, .after=1)

Merge3<-merged2 %>% 
  filter(Run == 2) %>% 
  left_join(annotated, by= "date") %>% 
  mutate(Bayes_status = if_else(is.na(GPP_mean), "Model Inconclusive", " Model Conclusive")) %>% 
  mutate(Discharge_Data = if_else(is.na(discharge), "Missing Discharge Data", "Have Discharge Data"))

```

```{r}
t4<-Merge3 %>% 
  group_by(data.check, Bayes_status) %>% 
  count() %>% 
  arrange(desc(Bayes_status))

pander::pander(t4,caption="^ Data Status: Bayes Output")

t5<-Merge3 %>% 
  group_by(Bayes_status, Discharge_Data) %>% 
  count() %>% 
  arrange(desc(Bayes_status))

pander::pander(t5,caption="^ Data Status: Discharge Availability")

t6<-Merge3 %>% 
  filter(Bayes_status == "Model Inconclusive") %>% 
  group_by(Bayes_status, data.check, Discharge_Data) %>% 
  count() %>% 
  arrange(desc(Discharge_Data))

pander::pander(t6,caption="^ Data Status: Discharge Availability")

```



# Visualize

## Prep Data

```{r}
# # assign sites
# run_sites <- c('NC_NHC')
# 
# filenames <- list.files("data/model_runs/Bayes/daily", pattern="*.csv", full.names = TRUE)
# 
# l <- lapply(filenames, read_csv)
# 
# short_names<-filenames %>%
#   str_remove("data/model_runs/Bayes/daily/") %>%
#   str_remove(".csv")
# 
# names(l)<-short_names
# 
# #bind l together to one larger data.table, by columnname, fill missing with NA
# dt <- data.table::rbindlist( l, use.names = TRUE, fill = TRUE, idcol=short_names) %>%
#   rename(source=1) %>%
#   mutate(Site = if_else(str_detect(source, "NC_NHC"), 'NHC', NA_character_),
#          .after=1)
# 
# write.csv(dt, "data/model_runs/Combined-Daily-Data.csv")
```


# Download Data

```{r}
data_raw<-read.csv("data/model_runs/Combined-Daily-Data.csv") %>% 
  mutate(date = as.POSIXct(as.Date(date))) %>% 
  mutate(year = year(date), .after = date)

plot_data<-data_raw %>% 
  filter(date < "2022-04-10") %>% # only looking at 2021
  filter(date > "2021-04-10") %>% 
  group_by(Site) %>% 
  filter(!is.na(GPP_mean)) %>% 
  mutate(cumGPP = cumsum(GPP_mean),
         cumER = -1*(cumsum(-1*ER_mean)))
```

# QA/QC

Count of days with no data

```{r}
missing_days<-data_raw %>% 
  group_by(year, valid_day) %>%
  count() %>% 
  ggplot(aes(x="", y=n, fill=valid_day)) +
  geom_col() + 
  geom_text(aes(label = n), position = position_stack(vjust=0.5)) +
  facet_wrap(~year) +
  coord_polar(theta = "y") + 
  theme_void() + labs(title = "Days with Data")

missing_days
```


# Plot Data

## Cumulative Plots

```{r}
NHC_metab<-plot_data %>% 
  filter(Site %in% c('NHC')) %>%
  ggplot(., aes(x = as.Date(date))) +
  geom_area(aes(y = cumGPP, fill = "GPP"))+
  geom_area(aes(y = cumER, fill = "ER"))+
  ylim(-2000, 500) + 
  theme_classic() +
  scale_fill_manual(name = element_blank(),
                   values = alpha(c('#C76C05', "#208D01"), 0.8)) + 
  scale_x_date(date_breaks = "1 month",
                 labels = label_date_short(format = c("%Y", "%b", NA, NA)),
                 expand = c(0.005,0.005)) +
  labs(x=element_blank(), y=element_blank(), title = "NHC") +
  theme(text = element_text(size = 20))

NHC_metab
ggsave("output/NHC_metab.png", width= 10, height= 6)

```

## Point Plots

```{r}
NHC_metab_p<-plot_data %>% 
  filter(Site %in% c('NHC')) %>%
  filter(valid_day == "TRUE") %>% 
  filter(GPP_daily_mean >= 0) %>% filter(ER_daily_mean <= 0) %>% 
  ggplot(., aes(x = as.Date(date))) +
  geom_point(aes(y = GPP_daily_mean, color = "GPP"))+
  geom_ribbon(aes(ymin= `GPP_daily_2.5pct`, ymax= `GPP_daily_97.5pct`, fill = "GPP"))+
  geom_point(aes(y = ER_daily_mean, color = "ER"))+
  geom_ribbon(aes(ymin= `ER_daily_2.5pct`, ymax= `ER_daily_97.5pct`, fill = "ER"))+
  ylim(-25, 5) + 
  theme_classic() +
  scale_color_manual(name = element_blank(),
                   values = alpha(c('#C76C05', "#208D01"), 0.8)) + 
  scale_fill_manual(name = element_blank(),
                   values = alpha(c('#C76C05', "#208D01"), 0.3)) + 
  scale_x_date(date_breaks = "1 month",
                 labels = label_date_short(format = c("%Y", "%b", NA, NA)),
                 expand = c(0.005,0.005)) +
  labs(x=element_blank(), y=element_blank(), title = "NHC") +
  theme(text = element_text(size = 20))

NHC_metab_p
ggsave("output/NHC_metabv2.png", width= 10, height= 6)

```

